Share Buyback and Equity Issue Anomalies Revisited

### 2016-02-17 index.Rmd
debugging

if(0) {
  CACHE <- car_table_cache(DATASET_INI$returns_by_event_monthly,
                           DATASET_INI$SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
  save("CACHE",file = "cache.Rdata")
}else {
  load("cache.Rdata")  
}
report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)

@@

**Note that it takes a few minutes (possibly five) to create and download the new paper - work in progress.**

@@

  list(
    returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report],
    DatesMonth = DATASET_INI$DatesMonth[,useonly_report],
    SDC = DATASET_INI$SDC[useonly_report,],
    subset = useonly_report
    #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
    #DatesMonth = DATASET_INI$DatesMonth,
    #SDC = DATASET_INI$SDC
  )
})
```

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
    car_table_cached(CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
    car_table_cached(CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

@@

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
    car_table_cached(CACHE,Low_feature_events)$results,
    car_table_cached(CACHE,High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

@@

feature_IRATStable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
    car_table_cached(CACHE,Low_feature_events)$results,
    car_table_cached(CACHE,High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

>>>>

#if(1) {
#  CACHE <- car_table_cache(DATASET_INI$returns_by_event_monthly,
#                           DATASET_INI$SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)
#  save("CACHE",file = "cache.Rdata")
#} else {
#  load("cache.Rdata")  
#}
report_months_cal = c(as.numeric(reported_times[1:(length(reported_times)-1)]),1)

@@

**Note that it takes a few minutes (possibly more than five) to create and download the new paper (work in progress). Please wait without changing any parameters until you are prompted to download the new paper.**

@@

  SDC = DATASET_INI$SDC[useonly_report,]
  returns_by_event_monthly = DATASET_INI$returns_by_event_monthly[,useonly_report]
  DatesMonth = DATASET_INI$DatesMonth[,useonly_report]

  CACHE <- car_table_cache(returns_by_event_monthly,
                         SDC$Event.Date,Risk_Factors_Monthly,formula_used = five_factor_model)

  list(
    CACHE = CACHE,
    returns_by_event_monthly = returns_by_event_monthly,
    DatesMonth = DatesMonth,
    SDC = SDC,
    subset = useonly_report
    #returns_by_event_monthly = DATASET_INI$returns_by_event_monthly,
    #DatesMonth = DATASET_INI$DatesMonth,
    #SDC = DATASET_INI$SDC
  )
})

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

@@

feature_IRATStable <- reactive({
  thesign = ifelse(input$characteristic_irats_sign, -1, +1)
  thefeature = thesign*DATASET_NEW()$SDC[[which(names(DATASET_NEW()$SDC) == input$characteristic_irats)]]  
  High_feature_events = which(scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used)) & !is.na(thefeature))
  Low_feature_events = which(scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used)) & !is.na(thefeature))
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
    car_table_cached(DATASET_NEW()$CACHE,Low_feature_events)$results,
    car_table_cached(DATASET_NEW()$CACHE,High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

@@

feature_IRATStable_index <- reactive({
  thefeature = Index_Score_rect()
  High_feature_events = (scrub(thefeature) >= quantile(thefeature[!is.na(thefeature)],1-as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  Low_feature_events = (scrub(thefeature) <= quantile(thefeature[!is.na(thefeature)],as.numeric(input$quantile_used_all)) & !is.na(thefeature))
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,Low_feature_events], DATASET_NEW()$SDC$Event.Date[Low_feature_events], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,High_feature_events], DATASET_NEW()$SDC$Event.Date[High_feature_events], Risk_Factors_Monthly)$results
    car_table_cached(DATASET_NEW()$CACHE,Low_feature_events)$results,
    car_table_cached(DATASET_NEW()$CACHE,High_feature_events)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  res
})

### 2016-02-17 report.Rnw
debugging

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Special table combining industry characteristics and High/Low of all additional variables
\small
<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
tmp = generate_industry_table(sec1,sec2,sec3,sec5,sec5,sec6)
latex_render_data_frame(
  round(tmp,1), 
  title = "Industry Characteristics",
  caption="Percentage of high and low subset companies for all industries for which we have at least 100 events in our sample.",
  label = "tbl:industriesAdditional",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 1,
  digits=1,
  lastSpecial=F,dorotate=T
)
@
\normalsize

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
rownames(secU$Under_IdioBB2)[1:2] <- c("high U-index", "low U-index")
latex_render_data_frame(
  round(secU$Under_IdioBB2[1:6,1:4],1), 
  title = "Relations across firm characteristics for Buybacks",
  caption="Relation between Under/Overvaluation and High/Low samples of the additional variables for buybacks. Numbers indicate percentage of firms in the row that are also categorized as noted in the columns.",
  label = "tbl:underidioallBB2",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=1,
  lastSpecial=F,dorotate=F
)

latex_render_data_frame(
  round(secU$Under_IdioBB_cor2,2), 
  title = "Correlations of Buybacks Characteristics",
  caption="Correlation between all of the buybacks characteristics considered and the U-index score. All scores are defined using the universe of all CRSP companies at the time of the announcement with data up to the month before the announcement.",
  label = "tbl:underidioallBBcor2",
  columns=NULL,
  bigtitleontop = T,
  show_rownames=TRUE,
  scale = 0.9,
  digits=2,
  lastSpecial=F,dorotate=F
)
@

@@

\begin{figure}[H]
\centering
<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=

IRATS_table_all_bb_plot = EU_IRATStable_bb
IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")]

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Special table combining industry characteristics and High/Low of all additional variables
\small
<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
if (0){
  tmp = generate_industry_table(sec1,sec2,sec3,sec5,sec5,sec6)
  latex_render_data_frame(
    round(tmp,1), 
    title = "Industry Characteristics",
    caption="Percentage of high and low subset companies for all industries for which we have at least 100 events in our sample.",
    label = "tbl:CEUrelations",
    columns=NULL,
    bigtitleontop = T,
    show_rownames=TRUE,
    scale = 1,
    digits=1,
    lastSpecial=F,dorotate=T
  )
}
@
\normalsize

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
if (0){
  rownames(secU$Under_IdioBB2)[1:2] <- c("high U-index", "low U-index")
  latex_render_data_frame(
    round(secU$Under_IdioBB2[1:6,1:4],1), 
    title = "Relations across firm characteristics for Buybacks",
    caption="Relation between Under/Overvaluation and High/Low samples of the additional variables for buybacks. Numbers indicate percentage of firms in the row that are also categorized as noted in the columns.",
    label = "tbl:underidioallBB2",
    columns=NULL,
    bigtitleontop = T,
    show_rownames=TRUE,
    scale = 0.9,
    digits=1,
    lastSpecial=F,dorotate=F
  )

  latex_render_data_frame(
    round(secU$Under_IdioBB_cor2,2), 
    title = "Correlations of Buybacks Characteristics",
    caption="Correlation between all of the buybacks characteristics considered and the U-index score. All scores are defined using the universe of all CRSP companies at the time of the announcement with data up to the month before the announcement.",
    label = "tbl:underidioallBBcor2",
    columns=NULL,
    bigtitleontop = T,
    show_rownames=TRUE,
    scale = 0.9,
    digits=2,
    lastSpecial=F,dorotate=F
  )
}
@

@@

\begin{figure}[H]
\centering
<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>= 
IRATS_table_all_bb_plot = EU_IRATStable_bb
IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")] <- -IRATS_table_all_bb_plot[rownames(IRATS_table_all_bb_plot) %in% as.character((-6):(-1)),which(colnames(IRATS_table_all_bb_plot)=="CAR")]

@@

\begin{figure}[H]
\centering
<< fig.width=10, fig.height=4, out.width='\\textwidth', echo=F >>=
#par(mfrow=c(2,1), mar=c(2.3,4,2.3,4))
#valuation_index_bb[which(valuation_index_bb==2)]<-3 # there is one company here. need to check why
tmp = table(secU$Index_score)
tmp = structure(as.numeric(tmp), .Names = names(tmp))
barplot(tmp,main = "", ylab = "Number of Announcements", xlab = "",las=2,space=0.5, cex.names=0.8)
#tmp = table(valuation_index_iss)
#tmp = structure(as.numeric(tmp), .Names = names(tmp))
#barplot(tmp,main = "SEOs", ylab = "Number of Announcements", xlab = "SEO Overvaluation Index",las=2,space=0.5, cex.names=0.8)
rm("tmp")
@
\caption{CEU-index. Distribution of the CEU-index of all buyback events.}
\label{fig:CEundervaluationindex}
\end{figure}
